### 2014-02-28 paper/formal.tex
switching cafe

\begin{definition}[Termination Sensitive Non-Interference (TSNI)]
  A language |(C, .->, erasef l)| is termination
  sensitive non-interfering if for any label |l|, and configurations
  |c1, c1', c2 member C|, if
  \begin{equation} \label{eq:tsni-lhs}
    |c1| \approx_{|l|} |c2|
    \qquad \text{and} \qquad
    |c1| |.->|^* |c1'|
  \end{equation}
  then there exists a configuration |c2' member C| such that
  \begin{equation} \label{eq:tsni-rhs}
    |c1'| \approx_{|l|} |c2'|
     \qquad \text{and} \qquad
    |c2| |.->|^* |c2'|
    \ \text{.}
  \end{equation}
\end{definition}

@@

>>>>

\begin{definition}[Termination Sensitive Non-Interference (TSNI)]
  A language |(C, .->, erasef l)| is termination
  sensitive non-interfering if for any label |l|, and configurations
  |c1, c1', c2 member C|, if
  \begin{equation} \label{eq:tsni-lhs}
    |c1| \approx_{|l|} |c2|
    \qquad \text{and} \qquad
    |c1| |.->|^* |c1'|
  \end{equation}
  then there exists a configuration |c2' member C| such that
  \begin{equation} \label{eq:tsni-rhs}
    |c1'| \approx_{|l|} |c2'|
     \qquad \text{and} \qquad
    |c2| |.->|^* |c2'|
    \ \text{.}
  \end{equation}
\end{definition}
%
In other words if we take two |l|-equivalent configurations, then for every
intermediate step taken by the first configuration, there is a corresponding
step that the second configuration can take to result in a configuration that
is |l|-equivalent to the first resultant configuration.
\Red{TODO: Do we want a commutative diagram to illustrate this?}

\begin{figure}
  Round robin:
\begin{code}
  roundrobin step (it1, it2, ldots)  = it2, ldots, it1
  roundrobin D (it1, it2, ldots)     = it2, ldots
  roundrobin N (it1, it2, ldots)     = it2, ldots
  roundrobin F (it1, it2, ldots)     = it2, ldots, it1
\end{code}
  Sequential:
\begin{code}
  seq step (it1, it2, ldots)     = it1, it2, ldots
  seq N (it1, it2, ldots)        = it1, it2, ldots
  seq D (it)                     = it
  seq D (it1, it2, ldots)        = it2, ldots
  seq F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
\end{code}
\caption{Round robin and sequential scheduling policies.\label{fig:scheduler}}
\end{figure}

Directly, we now show that our IFC language satisfies TSNI under a particular
scheduling policy.
%
Specifically, we consider the language under the round-robin scheduler
|roundrobinf| given in Figure~\ref{fig:scheduler}.

@@

In general TSNI will not hold for an arbitrary scheduler |alpha|.
%
For example, |specLang alpha (targetLang nop)| with a scheduler that inspects a
sensitive threads current state when deciding which thread to schedule next
will clearly not satisfy TSNI.
%
In Section~\toref{} we detail the preceise scheduler for which our
specification language is TSNI.
%
Here, we simply remark that even non-adversairal schedulers are not always safe.

Consider the sequential scheduling policy |seqf| given in
Figure~\ref{fig:scheduler}.
%
It is trivial to show that |specLang seqf (targetLang nop)| does not satisfy
TSNI.
%
\Red{HERE}
